### 2021-11-11 chapters/01-chapter-1.tex
txs auto checkin

 \section{Jadwal Pelaksanaan}
 \newsavebox\mybox
 \begin{lrbox}{\mybox}
     \begin{ganttchart}[
     vgrid={*{6}{draw=none}, dotted},
     x unit=.05cm,
     y unit title=.6cm,
     y unit chart=.6cm,
     time slot format=isodate,
     time slot format/start date=2016-09-01]{2021-09-01}{2022-04-30}
     \ganttset{bar height=.6}
     \gantttitlecalendar{year, month} \\
     \ganttbar[bar/.append style={fill=blue}]{Tahap 1}{2021-09-01}{2021-11-30}\\
     \ganttbar[bar/.append style={fill=blue}]{Tahap 2}{2021-10-01}{2021-11-15}\\
     \ganttbar[bar/.append style={fill=blue}]{Tahap 3}{2021-11-01}{2021-12-15}\\
     \ganttbar[bar/.append style={fill=blue}]{Tahap 4}{2021-12-15}{2022-03-01}\\
     \ganttbar[bar/.append style={fill=blue}]{Tahap 5}{2022-02-01}{2022-04-30}
     \end{ganttchart}
 \end{lrbox}

>>>>

 \section{Jadwal Pelaksanaan}
 \newsavebox\mybox
 \begin{lrbox}{\mybox}
     \begin{ganttchart}[
     vgrid={*{6}{draw=none}, dotted},
     x unit=.05cm,
     y unit title=.6cm,
     y unit chart=.6cm,
     time slot format=isodate,
     time slot format/start date=2016-09-01]{2021-09-01}{2022-04-30}
     \ganttset{bar height=.6}
     \gantttitlecalendar{year, month} \\
     \ganttbar[bar/.append style={fill=blue}]{Studi Literatur}{2021-09-01}{2021-11-30}\\
     \ganttbar[bar/.append style={fill=blue}]{Analisis Masalah}{2021-10-01}{2021-11-15}\\
     \ganttbar[bar/.append style={fill=blue}]{Perancangan Solusi}{2021-11-01}{2021-12-15}\\
     \ganttbar[bar/.append style={fill=blue}]{Implementasi}{2021-12-15}{2022-03-01}\\
     \ganttbar[bar/.append style={fill=blue}]{Pengujian dan Analisis Hasil}{2022-02-01}{2022-04-30}
     \end{ganttchart}
 \end{lrbox}
